---
title: "Assignment #8"
author: "Anna Ehrhorn"
version: 1.0
date: "April 4, 2020"
output: html_notebook
---


*The assignment is focusing on our continued learning of knowledge and skills*
*related to function developmental and application, and Geoms.*


***
### Question 1

My challenge is to construct a function that will create an extra column 
to sum total score of a likert score while accounting for revere scored items.

Required within the function are the following:

*Data frame with rows indicating individuals and columns indicating items.

*A numeric indicating the scale used for the items.

*A numeric vector to indicate which items to be revered scored when summing 
scores to calculate the total score.

```{r}
surv.tot.score <- function(my.surv.data, scale.num, vector.num){
  # Changing to a matrix
  matrix.surv.data <- as.matrix(my.surv.data)
  
  # Score vectors identified as vector.num as mirror-lower
  reg.score.items <- matrix.surv.data[,!vector.num]
  rev.score.items <- matrix.surv.data[,vector.num]
  
  reg.score <- sum(reg.score.items)
  rev.score <- sum(scale.num - rev.score.items)
  
  # Add together score of each item for each individual
 for(matrix.surv.data[, 1:ncol], matrix.surv.data[1:nrow,]){
    # Sum of regular and reversed scored items
    sum.tot.score <- reg.score + rev.score
    return(sum.tot.score)
  }
  
  # Add on column of sum.tot.score to matrix
  matrix.surv.data.2 <- cbind(matrix.surv.data, sum.tot.score)
  
  # Convert to data.frame
  my.surv.data.2 <- as.data.frame(matrix.surv.data.2)

  return(write.csv(my.surv.data.2, col_names = TRUE))
}
```


***
### Question 2

Using the *Survey Data* to test out the function, *surv.tot.score*, that will print 
out a CSV file which contains the orginal data with the total score added. 

```{r include=FALSE}
library(here)

survey.data <- read.csv(here("Data", "survey.csv"))
```

```{r}
surv.tot.score(survey.data, 6, survey.data["item_3", "item_5", "item_6"])
```


***
### Question 3

Constructing a single scatter plot showing the relationship of science scores
to math scores by gender using hsb2 data and ggplot.

```{r include=FALSE}
library(tidyverse)
library(here)

hsb2 <- read_csv(here("Data", "hsb2.csv"))

problems(hsb2)
```

```{r}
ggplot(data = hsb2) +
  geom_point(mapping = aes(x = science, y = math, color = female)) +
  labs(x = "Standardized Science Score", y = "Standardized Math Score", 
  title = "Relationship between Science and Math Scores by Gender")
  
# Unsure of how to rename legend to "Gender" and make two different colors/shapes
  
  
```


***
### Question 4

This scatterplot is showing the same relationship, but with each gender with a 
seperate scatterplot.

```{r}
ggplot(data = hsb2) +
  geom_point(mapping = aes(x = science, y = math)) +
  labs(x = "Standardized Science Score", y = "Standardized Math Score", 
  title = "Relationship between Science and Math Scores by Gender") +
  facet_grid( ~ female)
```


***
### Question 5

A graph created using the *geom_boxplot* to illustrate math scores for each 
socioeconomic status level.

```{r}
ggplot(data = hsb2) +
  geom_boxplot(mapping = aes(x = ses, y = math, fill = ses, group = ses)) +
  labs(x = "Socioeconomic Status (from Low to High)", y = "Math Standard Score", 
  title = "Math Scores by Socioeconomic Status")
```

